The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-03-22 paper/main.tex
Upadated some equations.

\begin{algorithm}[H]
\captionof{algorithm}{Data Collection Algorithm}\label{algo:data_collection_algo}
\begin{algorithmic}[1]
\While{$i < 1000$} 
\State $i \gets i + 1$
\State $word \gets random(word\_list)$
\State $repos \gets git\_search(word)$
\State $j \gets $%\Call{random}{0... \Call{size}{repos}}$
\State $repo \gets repos_j$
\State %\Call{store}{repo}
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\subsection{Analysis}
Where the Set $S$ is the random GitHub repository sample. Each randomly collected repository $S_i$ contains a Set of attributes $A$. Thus, a set of attributes for a given repository can be referred to as $A_{S_i}$.

Given the total set of attributes $A$, each individual attribute set can be denoted as $A_j$. Each individual attribute processed by some aggregate function $f$, or $f(  A_j )$. For this analysis, the aggregate functions are: \textsc{mean}, \textsc{min}, \textsc{max}, \textsc{stddev}. This analysis is applied to all $n$ repositories for which data was collected. Results were then averaged over all repositories. Each attribute is analyzed independently, so given:
\[ g(j) = \frac{\sum\limits_{i=1}^{n} f(  A_{S{_i}j}  ) } {n} \]
each individual attribute is processed via $g(j)$ and will result in the average of the given aggregate function.

The individual attributes of $A$, or $A_j$, are described below. For detailed summary statistics of these attributes, see Figure  \ref{table:summary_stats}.\\\\
\noindent \textbf{\textit{Issues:}}
The number of issues posted to a repository's issue tracker\footnote{https://github.com/blog/411-github-issue-tracker}.

@@

The average is calculated using the following method. Let $d(x)$ be a function that converts seconds to a Date, and let $s(x)$ be a function that converts a Date to seconds. The variable $n$ denotes the total number of issues, or $I$, assigned to a particular repository.

\[ \tau = d\left( \frac{\sum_{i=1}^{n} s(C_{I_i} ) - s(O_{I_i} )  } {n} \right) \]

For each issue $I_i$ in $I$, the \textsc{opened\_date} $O_{I_i}$ is subtracted from the \textsc{closed\_date} $C_{I_i}$. The result of this is averaged and converted into a date via $d(x)$, resulting in the average issue close time interval $\tau$.

@@

\subsection{Research Questions}
\textbf{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\
The data in figure \ref{fig:committers_percentage_pie_chart} represents commit percentage breakdown. The inner percentages represent the percentage of committers in a project that that have committed the outer percentage amount of commits to that project, or

 \[ P = \left\{ \frac{ C_u } { |C| } \times 100 \Big| u \in U \right\} \]

@@

where, given the set of commits of a repository $C$ and the set of committers to the repository $U$, the commits by each user $C_u$ are divided by the total number of commits $|C|$, yielding the set of contribution percentages $P$ for the repository. Elements of $P$ are then assigned to ranges $0-5\%$, $5-10\%$, $10-50\%$, $50-95\%$, and $95-100\%$ (with shared values inclusive to the larger range). The distribution of this range assignments is plotted on Figure \ref{fig:committers_percentage_pie_chart}.

>>>>

\begin{algorithm}[H]
\captionof{algorithm}{Data Collection Algorithm}\label{algo:data_collection_algo}
\begin{algorithmic}[1]
\While{$i < 1000$} 
\State $i \gets i + 1$
\State $word \gets random(word\_list)$
\State $repos \gets git\_search(word)$
\State $j \gets $%\Call{random}{0... \Call{size}{repos}}$
\State $repo \gets repos_j$
\State \Call{store}{repo}
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\subsection{Analysis}
In this context, a \textit{Repository} is defined as a Set of \textit{Attributes}. An \textit{Attribute} is a metric of interest. See Section \ref{sec:attributes} for further information on individual \textit{Attributes}. These metrics of interest are used as an Indexing Set $A^\prime$, and have labels as follows:

\[A^\prime = \{i, c, i^\prime, i^{\prime\prime}, \Delta, \alpha, \beta\}\]

Where $i$ = {\textit{Issues}, $c$ = {\textit{Commits}, $i^\prime$ = {\textit{Closed Issues}, $i^{\prime\prime}$ = {\textit{Open Issues}, $\Delta$ = {\textit{Issue Close Time}, $\alpha$ = {\textit{Issue Creators}, and $\beta$ = {\textit{Committers}.

All analyzed \textit{Respositories} can be thought of as the Indexed Family of \textit{Attribute} Sets $A$, or a Set of Sets of \textit{Attributes}. Let the Set of these Sets of \textit{Attribute} Sets be called $S$, or the \textit{Repository Sample}. We can label the \textit{Attribute} Sets by arbitrary integers 0 through $|S|$, or:
\[ \{A_i\}_{i \in \{0,1,2 ... |S|\} }\]

In this way, we can reference a Set of \textit{Attributes} (or, an individual \textit{Repository}), by $A_i$.

Going further, we can also denote an individual \textit{Attribute} of a given \textit{Repository} by:
\[ \{A_{(i,r)}\}_{(i,r) \in A^\prime \times \{0,1,2 ... |S|\} } \]
or, $A_{i,r}$. For example, $A_{\Delta,10}$ would denote the value of the \textit{Issue Close Time} ($\Delta$) of Repository \textit{10}.

Each individual Attribute processed by some aggregate function $f$, or $f(  A_{i,r} )$. For this analysis, the aggregate functions are: \textsc{mean}, \textsc{min}, \textsc{max}, \textsc{stddev}. This analysis is applied to all $n$ repositories for which data was collected. Results were then averaged over all repositories. Each attribute is analyzed independently, so given:
\[ g(j) = \frac{\sum\limits_{r = 0}^{|S|} f(  A_{r,j}  ) }{|S|} \]
each individual attribute is processed via $g(j)$ and will result in the average of the given aggregate function.

\subsubsection{Attributes}
\label{sec:attributes}
The individual \textit{Attribute} names, or the elements of $A^\prime$, are described below. For detailed summary statistics of these \textit{Attributes}, see Figure  \ref{table:summary_stats}.\\\\
\noindent \textbf{\textit{Issues:}}
The number of issues posted to a repository's issue tracker\footnote{https://github.com/blog/411-github-issue-tracker}.

@@

The average is calculated using the following method. Let $d(x)$ be a function that converts seconds to a Date, and let $s(x)$ be a function that converts a Date to seconds. Let $I$ equal the Set of \textit{Issues} in a given repository, with elements comprised of tuples $(\tau, \tau^\prime)$, where $\tau$ is \textit{Issue Open Time} and $\tau^\prime$ is \textit{Issue Close Time}. We calculate \textit{Issue Close Time} by:

\[ \Delta = d\left( \frac{\sum_{i \in I} s( p_{(1)}i ) - s( p_{(2)}i )  } {n} \right) \]

Where for each issue $i$ in $I$, the \textit{Issue Open Date} $s( p_{(1)}i)$ is subtracted from the \textit{Issue Close Date} $s( p_{(2)}i)$, and $p_{(1)}i$ and $p_{(2)}i$ denote the elements of the tuple, or \textit{Issue Open Date} and \textit{Issue Close Date}, respectively. The result of this is averaged and converted into a Date via $d(x)$, resulting in the average issue close time interval $\Delta$.

@@

\subsection{Research Questions}
\textbf{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\
The data in figure \ref{fig:committers_percentage_pie_chart} represents commit percentage breakdown. The inner percentages represent the percentage of committers in a project that that have committed the outer percentage amount of commits to that project, or:

\begin{equation}
P = \left\{ \frac{ C_u } { |C| } \times 100 \Big| u \in U \right\}
\label{eq:commit_percentage}
\end{equation}

Where $U$ is the Set of \textit{Committers} to a given \textit{Repository} and $C$ is the MultiSet of \textit{Commits} by an individual \textit{Committers} to a given \textit{Repository}, or:
 \[ \{ C_u \}_{u \in U} \]

@@

To find the percentages Set $P$ of equation\ref{eq:commit_percentage}, the commits by each user $C_u$ are divided by the total number of commits $|C|$, yielding the set of contribution percentages $P$ for the repository. Elements of $P$ are then assigned to ranges $0-5\%$, $5-10\%$, $10-50\%$, $50-95\%$, and $95-100\%$ (with shared values inclusive to the larger range). The distribution of this range assignments is plotted on Figure \ref{fig:committers_percentage_pie_chart}.
